Hydras, Ordinals \& Co. \\ A library in Coq of entertaining formal mathematics

### 2021-10-13 doc/JFLA2022/paper.tex
basic dependency elements

In 2020, members of \community transferred the Gaia source code to GitHub and adapted it for recent releases of the Mathematical Components library, which Gaia heavily relies on. A volunteer finished the only in-progress proof left by Grimm. At around 165,000 lines of code, Gaia is currently one of the largest maintained open source Coq projects~\cite{Gaia}.

@@

\node[rectangle, draw=black,minimum height=0.5cm,minimum width=1.5cm] (cantor) { Cantor };
\node[rectangle, draw=black,minimum height=0.5cm,minimum width=1.5cm,right of=cantor, node distance=3cm] (additions) { Additions };
\node[rectangle, draw=black,minimum height=0.5cm,minimum width=1.5cm,right of=additions, node distance=3cm] (additions) { Goedel };

>>>>

In 2020, members of \community transferred the Gaia source code to GitHub and adapted it for recent releases of the Mathematical Components library, which Gaia heavily relies on. Volunteers (``collaborators of Nicolas Bourbaki'') then finished the only in-progress proof left by Grimm. At around 165,000 lines of code, Gaia is currently one of the largest maintained open source Coq projects~\cite{Gaia}.

@@

\begin{scope}[xshift=-6cm]
\node[rectangle, dotted,draw=black,minimum height=0.5cm,minimum width=1.5cm] (additions) { Additions };
\node[rectangle, dotted,draw=black,minimum height=0.5cm,minimum width=1.5cm,right of=additions, node distance=2cm] (goedel) { Goedel };
\node[rectangle, dotted,draw=black,minimum height=0.5cm,minimum width=1.5cm,right of=goedel, node distance=2cm] (cantor) { Cantor };
\end{scope}

\begin{scope}[yshift=-0.7cm,xshift=0.25cm]
\node[rectangle, draw=black,dashed,minimum height=0.5cm,minimum width=1.5cm] (equations) { Equations };
\node[rectangle, draw=black,dashed,minimum height=0.5cm,minimum width=1.5cm,right of=equations, node distance=2cm] (mathcomp) { MathComp };
\node[rectangle, draw=black,minimum height=0.5cm,minimum width=1.5cm,node distance=2cm,right of=mathcomp, node distance=2cm] (paramcoq) { Paramcoq };
\end{scope}

\begin{scope}[yshift=-1.8cm,xshift=-4cm]
\node[rectangle, draw=black,minimum height=0.5cm,minimum width=1.5cm] (hydras) { Hydra-battles };
\node[rectangle, draw=black,minimum height=0.5cm,minimum width=1.5cm,right of=hydras, node distance=2.5cm] (chains) { Addition-chains };
\node[rectangle, draw=black,minimum height=0.5cm,minimum width=1.5cm,right of=chains, node distance=2.2cm] (gaia) { Gaia };
\end{scope}

\begin{scope}[yshift=-2.8cm,xshift=-6cm]
 \node[rectangle, draw=black,minimum height=0.5cm,minimum width=1.5cm] (goedelcc) { Goedel };
 \node[rectangle, draw=black,minimum height=0.5cm,minimum width=1.5cm,right of=goedelcc, node distance=2.2cm] (gaiahydras) { Gaia-hydras };
\end{scope}
